Table 1

### 2017-06-29 doc/RMD/table-1.Rmd
remove as-is output so it's easier to see on github
update table-1.Rmd to account for the new column

```{r isolate_table, results = "asis"}
library("readr")
library("dplyr")
library("huxtable")

clmn <- cols(
  .default = col_integer(),
  Region = col_character(),
  Source = col_character(),
  Host = col_character()
)

>>>>

```{r isolate_table, comment = NA}
library("readr")
library("dplyr")
library("huxtable")

clmn <- cols(
  .default = col_integer(),
  Severity = col_double(),
  Region = col_character(),
  Source = col_character(),
  Host = col_character()
)
